Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-09-07 doc/main_jfm.tex
working on conclusions

Figure~\ref{figure12} shows numerical results when the centroids of the
two Janus particles are placed at $(-10,-0.1)$ and $(10,0.1)$ (case
(iii) from Figure~\ref{figure11}). With this setup, the two JP vesicles
eventually separate along the $\pm y$-directions and we compare the
results against a continuum model as shown in all insets. Panels
(b)--(d) show the transient behavior of the JP vesicles and the
continuum vesicles under an extensional flow. In both the coarse-grained
model and the continuum model, the vesicles initially converge towards
one other and then diverge along the $y$-axis. The behavior of the
streamlines in both cases are similar. The pressure is initially largest
in the gap formed by two JP vesicles and decreases during the
separation. The short range repulsion plays an important role to avoid
structure collisions.
%and this result can be
%compared with some findings in continuum modeling simulations.

@@

This study proposes a continuum coarse-grained model for JP vesicle that focuses on the 
hydrophobic interactions between lipids and hydrodynamic interactions.
The mobility problem using integral equation methods combines the previously introduced HAP and the 
revised hydrophobic force for obtaining particle dynamics.

The imposed forces and torques of JP system adopt not only HAP but also a newly developed short 
range repulsion given by \ref{eq:REPULforce} and \ref{eq:REPULtorque}.
The hydrodynamic stress tensor calculated in the algorithm leads to examinations of permeable 
membrane where the stretching modulus $K_A$ and the permeability constant $P$ can be obtained.
%
With the use of selected parameters, the numerical algorithm yields good qualitative results such as
phenomena in tank-treading JP vesicle. The reduced area $A^*$ decreases as the shear rate increases
 and we measure the equilibrium reduced area for a number of shear rates. The results show that the total
 length of JP vesicle is conserved and the decay rate of the reduced area is independent of shear rates when shear rates $\dot\gamma$ are between $\sim0.005$ ns$^{-1}$ and $0.008$ ns$^{-1}$.
Moreover, the proposed model can capture the membrane rupture when the shear flow is at a high shear rate
and this makes a breakthrough about having an idea for simulating such phenomenon different from other continuum modeling simulations when the bilayer membrane is represented as a closed and continuous curve.

Inter-monolayer friction coefficients $b$ are then obtained and reported by calculating the friction force $F_f$
using pressure jumps and slip velocities with respect to the bilayer midplane.
The resulting friction coefficients $b$ are about one order of magnitude smaller than ones in
~\cite{denOtter2007} and this observation suggests that the granularity of the system is a factor of having 
the discrepancy. The coarse-graining level of the JP vesicle has much longer length scale comparing against
the molecular dynamics simulations, in addition, the repulsive potential creates gaps between JP where the 
error in slip velocities piles up over the computational time.

We also study the migration of a JP vesicle suspended in a parabolic flow and obtain the asymmetric slipper shape. The reduced area $A^*$ of the starting JP vesicle is close to 1 and $A^*=0.9$ at the equilibrium
state. A qualitative agreement has been made comparing with the two-dimensional inextensible membrane in continuum modeling simulations presented in~\cite{Kaoui09}. An interesting outcome is that the mean
$y$-position of the JP vesicle performs an oscillatory motion toward the center of the Poiseuille flow and this
may be caused by the granularity of the JP vesicle and choices of model parameters.

Results of two JP vesicles suspended in both shear and extensional flows have outstanding agreements with ones generated using continuum modeling in streamlines comparisons.
For two JP vesicles in shear flow, a demonstration of rotating behavior is presented and two overlapping 
trajectories of two centroid are observed as expected when two starting centroids are placed on the same 
horizontal level. The hydrophobic action and the repulsive potential lead to an adhesive effect when two 
JP bilayers are within a short distance.
We provide a series of results when two JP vesicles are suspended in extensional flow. We obtain similar results to the ones in \cite{qua-vee-you2019} when the reduced area $A^*$ is high and both centroids are placed 
with some vertical displacements.

Our future goal is to extend the current framework to a three-dimensional JP vesicle system. 
The further implementation of adding a fast algorithms such as the fast multipole method is also a 
practical approach.
Having a more physical boundary conditions on JP boundaries with experimental data is a reasonable direction and the future comparison with the laboratory experiments can be accomplished.

>>>>

Figure~\ref{figure12} shows numerical results when the centroids of the
two Janus particles are placed at $(-10,-0.1)$ and $(10,0.1)$ (case
(iii) from Figure~\ref{figure11}). With this setup, the two JP vesicles
eventually separate along the $\pm y$-directions and we compare the
results against a continuum model as shown in all insets. Panels
(b)--(d) show the transient behavior of the JP vesicles and the
continuum vesicles under an extensional flow. In both the coarse-grained
model and the continuum model, the vesicles initially converge towards
one other and then diverge along the $y$-axis. The behavior of the
streamlines in both cases are similar. The pressure is initially largest
in the gap formed by two JP vesicles and decreases during the
separation. The short-range repulsion plays an important role to avoid
structure collisions.
%and this result can be
%compared with some findings in continuum modeling simulations.

@@

This study presents a continuum coarse-grained model for JP vesicles
that focuses on the hydrophobic interactions between coarse-grained
lipids and hydrodynamic interactions. In contrast to molecular dynamic
simulations, the hydrophobic interactions exhibit the self-assembly
property of the lipid bilayer membrane. The proposed energy potential
combined with the mobility problem for rigid body motions captures
membrane mechanics including deformations, stretching modulus, and the
permeability of a JP membrane. This work is highly applicable with
fields in material science and condensed matter physics such as Janus
colloids~(\cite{Bradley2017,Mallory2017}) and the setup can be tuned to
match experimental results such as the morphology of colloid
surfactants~(\cite{Bradley2016}).

Integral equation methods are used to solve the mobility problem and the
previously introduced HAP model that determines the forces and torques
of the individual rigid bodies. In addition to the HAP forces and
torques, we impose a short-range repulsion to avoid unphysical contact.
Our method requires calculations of the hydrodynamic stress tensor, and
this is leads to examinations of the membrane permeability constant $P$
and the membrane stretching modulus $K_A$. With the use of suitable
parameters, the numerical results yield good qualitative phenomena such
as a tank-treading JP vesicle. The reduced area $A^*$ decreases as the
shear rate increases and we measure the equilibrium reduced area for
various shear rates. The results show that the total length of a JP
vesicle is conserved and the decay rate of the reduced area is
independent of the shear rate values  between $0.005$~ns$^{-1}$
and~$0.008$ ns$^{-1}$. Moreover, the proposed model can describe
membrane rupture in high shear rates. Therefore, our methods can be
applied to vesicles undergoing topological changes which is not
difficult to simulate when using a continuum model that represents
vesicles as closed and continuous curves.

Our coarse-grained model is also able to calculate inter-monolayer
friction. The inter-monolayer friction coefficients are determined by
calculating the tangential friction force and slip velocities with
respect to the bilayer midplane. The resulting friction coefficients $b$
are about one order of magnitude smaller than those reported
by~\cite{denOtter2007}, and this discrepancy is partially due to the
granularity of the model. In addition, the coarse-graining level of the
JP vesicle has a much larger length scale than molecular dynamics
simulations, and the repulsive force creates gaps between Janus
particles where the error in slip velocities accumulates over time.

We also study the spatial migration of a JP vesicle suspended in a
parabolic flow. The chosen parameter values results in an asymmetric
slipper shape. A qualitative agreement has been made comparing with the
two-dimensional inextensible membrane in continuum modeling
simulations~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}). The
initial reduced area of the JP vesicle is $A^* \approx 1$ and the
equilibrium reduced area is $A^*=0.9$. An interesting result of the JP
vesicle is that the mean $y$-position oscillates toward the center of
the Poiseuille flow and this may be caused by the granularity of the JP
vesicle and choices of the model parameters.

\todo[inline]{Bryan left off here}
Results of two JP vesicles suspended in both shear and extensional flows
have outstanding agreements with ones generated using continuum modeling
in streamlines comparisons. For two JP vesicles in shear flow, a
demonstration of rotating behavior is presented and two overlapping
trajectories of two centroid are observed as expected when two starting
centroids are placed on the same horizontal level. The hydrophobic
action and the repulsive potential lead to an adhesive effect when two
JP bilayers are within a short distance. We provide a series of results
when two JP vesicles are suspended in extensional flow. We obtain
similar results to the ones in \cite{qua-vee-you2019} when the reduced
area $A^*$ is high and both centroids are placed with some vertical
displacements.

Our future goal is to extend the current framework to a
three-dimensional JP vesicle system. The further implementation of
adding a fast algorithms such as the fast multipole method is also a
practical approach. One ongoing work is to add thermal fluctuations onto
Janus particles to obtain Brownian dynamics is crucial for obtaining
membrane diffusion. Having a more physical boundary conditions on JP
boundaries with experimental data is a reasonable direction and the
future comparison with the laboratory experiments can be accomplished.
